### 2016-11-04 text/ms.Rmd
Update paper to deal with rest of reviewer comments

We can exploit these characteristics by using the predictions from a group of
models as inputs into a separate statistical model. This technique, sometimes
called superensemble modelling [@krishnamurti1999], is common in climate and
weather forecasting [e.g., @yun2005; @mote2015]. The superensemble is fit to a
training dataset where outcomes are well known and then used to predict on a
dataset of interest. For example, @krishnamurti1999
combined predictions of wind and precipitation in Asian monsoons via a
superensemble regression fit to observed data. Their superensemble was
considerably more accurate than any individual prediction or weighted average
of predictions.

@@

We first developed and tested ensemble methods on a fully factorial simulated
dataset of fisheries with known status [@rosenberg2014]. 
Briefly, these simulations were implemented 
with the FLR packages [@kell2007] 
for the statistical software R, and, in particular, the FLBRP package.
The framework takes a series of 
life-history parameters and fishery characteristics
to generate population projections
and resulting catch timeseries.
Life-history values (e.g. mean asymptotic length)
for three fish life histories (small pelagic,
demersal, and large pelagic) 
were translated into a complete set of parameters for
a von Bertalanffy growth model,
a maturity ogive,
natural mortality, 
a selectivity function,
and a Beverton-Holt stock-recruitment function\R{A4}
using the life-history relationships derived in @gislason2008.
Fishing scenarios included three levels of initial biomass depletion
compared to carrying capacity: biomass at 100%, 70%, and 40% of carrying
capacity; and four exploitation patterns: (1) a constant exploitation rate,
(2) an exploitation rate coupled with biomass to mimic an open-access
single-species fishery, (3) a scenario where exploitation rate increased
continuously, and (4) a "roller-coaster" scenario where the exploitation
rate increased and then decreased. Process noise (recruitment variability;
i.e., unexplained variability in population dynamics) was introduced to the
models at two magnitudes in log space, $N(0, 0.2^2)$ and $N(0, 0.6^2)$,
and was either uncorrelated through time or had first-order autoregressive
correlation of $0.6$. The simulation also included a scenario with $N(0,
0.2^2)$ measurement error around log(catch) and one scenario without
measurement error. @rosenberg2014 ran ten iterations for each combination
of factors adding stochastic draws of recruitment and catch-recording
variability each time to generate a total of 5760 stocks. 
Code to generate the simulations is available at
<https://github.com/iagomosqueira/stockStatusFAO> (last accessed 2016-09-27).

@@

Superensemble models allow us to incorporate additional covariates and
potentially leverage interactions between these covariates and individual model
predictions. Additional covariates could be, for example, life-history
characteristics, information on exploitation patterns, or statistical
properties of the data. We tested the performance benefits of including one set
of additional covariates: spectral properties of the catch time series.
Spectral analysis decomposes a time series into the frequency domain and
provides a means of describing the cyclical shape of the catch series that is
independent of time series length (except in affecting precision) and
independent of absolute magnitude of catch. We fit spectral models to the
scaled catch time series (catch divided by maximum catch) with the `spec.ar`
function in R and recorded representative short- and long-term spectral
densities at frequencies of 0.20 and 0.05, which correspond to 5- and 20-year
cycles. For the linear model superensemble, we incorporated the two spectral
covariates (S1, S2) along with all second-order interactions as:\R{D}

\begin{equation}
\hat{\theta_i} = \beta_0 + \beta_1 \hat{b}_{i,1} + ... +
\beta_{1,2} \hat{b}_{i,1} \hat{b}_{i,2} + ... +
\beta_{S1} S1_i + 
\beta_{S2} S2_i + 
\beta_{1,S2} \hat{b}_{i,1} S2_i + ... +
\epsilon_i,
\end{equation}

@@

We also tested our ensemble methods on the RAM Legacy Stock Assessment Database
--- a compilation of stock-assessment output from hundreds of exploited marine
populations around the world. Our analysis of the stock-assessment database was
based on version 2.5. After removing stocks for which at least one of the
individual models described below did not converge (121), this database
included `r ram_stocks_n` stocks. We removed these stocks for all methods ---
both for the individual and superensemble models. An alternative would be to
fit separate superensemble models to subsets of the individual models that did converge,
but for simplicity we will only use superensemble models fitted to all four
individual models.\R{A6}

@@

@@

A strength of superensembles is that they can be tailored to predict specific
response variables. For example, we built separate superensemble models of mean
$B/B_\mathrm{MSY}$ and the slope of $B/B_\mathrm{MSY}$. The same set of model
weights or non-linear relationships need not hold across different response
variables. For instance, SSCOM contributed little to the GBM superensemble
estimate of status at higher levels of predicted $B/B_\mathrm{MSY}$ (Fig.
\ref{partial-sim}), but contributed strongly to estimates of trend (Fig.
\ref{partial-sim-slope}). Formally, fitting superensemble models to specific
quantities of interest (such as the slope of $B/B_\mathrm{MSY}$) provides an additional
calibration step to a quantity of interest [@rykiel1996].\R{A10}
This ensemble calibration could include a loss function
tailored to the goals of the model, say placing greater weight on accuracy at
lower rather than higher status levels. Conversely, because superensembles are
tailored to a specific response and loss function, superensembles force a
modeller to choose an operational purpose for their model up front [*sensu*
@dickey-collas2014].

As @box1987 noted, all models are wrong, but some may still be useful. The
ensemble methods we investigated attempt to piece together the useful parts of
candidate models to build a model with improved performance. Instead of viewing
the superensemble as a black box, we think considerable mechanistic
understanding can be gained by studying its structure. For example, when SSCOM
estimates low status this is likely the case, conversely when COMSIR
estimates low status, the true status is more likely to be high (Fig.
\ref{partial-sim}). These models have two main differences: (1) the form of
effort dynamics and (2) the allowance for both measurement and process error in
SSCOM, whereas the implemented COMSIR admits measurement error only. Were the
methods to differ only in effort dynamics, the results point towards a more
suitable representation of effort dynamics at low biomasses in SSCOM. We think
that such investigation of the structure of a superensemble may lead to
improvement in the mechanisms assumed in the individual models.

@@

@@

We thank members of Phase I of the working group "Developing new approaches to
global stock status assessment and fishery production potential of the seas"
who contributed to developing the data-limited methods and simulations used in
our analysis. We thank E. Jardim, F. Scott, and J.A. Hutchings for helpful
comments during the development of this project, and R.D. Methot for comments
on an earlier version of the manuscript. A.A. Rosenberg is president of MRAG
Americas Inc, a consulting company specializing in fisheries science. We thank
the Gordon and Betty Moore Foundation for funding the working group "Applying
data-limited stock status models and developing management guidance for
unassessed fish stocks".

>>>>

We can exploit these characteristics by using the predictions from a group of
models as inputs into a separate statistical model. This technique, sometimes
called superensemble modelling [@krishnamurti1999], is common in climate and
weather forecasting [e.g., @yun2005; @mote2015]. The superensemble is fit to a
training dataset where outcomes are well known and then used to predict on a
dataset of interest. For example, @krishnamurti1999
combined predictions of wind and precipitation in Asian monsoons via a
superensemble regression fit to observed data. Their superensemble was
considerably more accurate than any individual prediction or an average
of the predictions.

@@

We first developed and tested ensemble methods on a fully factorial simulated
dataset of fisheries with known status [@rosenberg2014]. 
Briefly, these simulations were implemented 
with the FLR packages [@kell2007] 
for the statistical software R, and, in particular, the FLBRP package.
The framework takes a series of 
life-history parameters and fishery characteristics
to generate population projections
and resulting catch timeseries.
Life-history values (e.g. mean asymptotic length)
for three fish life histories (small pelagic,
demersal, and large pelagic) 
were translated into a complete set of parameters for
a von Bertalanffy growth model,
a maturity ogive,
natural mortality, 
a selectivity function,
and a Beverton-Holt stock-recruitment function\R{A4}
using the life-history relationships derived in @gislason2008.

Fishing scenarios included three levels of initial biomass depletion
compared to carrying capacity: biomass at 100%, 70%, and 40% of carrying
capacity; and four exploitation patterns: (1) a constant exploitation rate,
(2) an exploitation rate coupled with biomass to mimic an open-access
single-species fishery, (3) a scenario where exploitation rate increased
continuously, and (4) a "roller-coaster" scenario where the exploitation
rate increased and then decreased. Process noise (recruitment variability;
i.e., unexplained variability in population dynamics) was introduced to the
models at two magnitudes in log space, $N(0, 0.2^2)$ and $N(0, 0.6^2)$,
and was either uncorrelated through time or had first-order autoregressive
correlation of $0.6$. The simulation also included a scenario with $N(0,
0.2^2)$ measurement error around log catch  and one scenario without
measurement error. @rosenberg2014 ran ten iterations for each combination
of factors adding stochastic draws of recruitment and catch-recording
variability each time to generate a total of 5760 stocks. 
Code to generate the simulations is available at
<https://github.com/iagomosqueira/stockStatusFAO> (last accessed 2016-09-27).

@@

Superensemble models allow us to incorporate additional covariates and
potentially leverage interactions between these covariates and individual model
predictions. Additional covariates could be, for example, life-history
characteristics, information on exploitation patterns, or statistical
properties of the data. We tested the performance benefits of including one set
of additional covariates: spectral properties of the catch time series.
Spectral analysis decomposes a time series into the frequency domain and
provides a means of describing the cyclical shape of the catch series that is
independent of time series length (except in affecting precision) and
independent of absolute magnitude of catch. We fit spectral models to the
scaled catch time series (catch divided by maximum catch) with the `spec.ar`
function in R and recorded representative short- and long-term spectral
densities at frequencies of 0.20 and 0.05, which correspond to 5- and 20-year
cycles. For the linear model superensemble, we incorporated the two spectral
covariates ($S1$, $S2$) along with all second-order interactions as:\R{D}

\begin{equation}
\hat{\theta_i} = \beta_0 + \beta_1 \hat{b}_{i,1} + ... +
\beta_{1,2} \hat{b}_{i,1} \hat{b}_{i,2} + ... +
\beta_{S1} S1_i + 
\beta_{S2} S2_i + 
\beta_{S1,S2} S1_i S2_i + 
\beta_{1,S2} \hat{b}_{i,1} S2_i + ... +
\epsilon_i,
\end{equation}

@@

We also tested our ensemble methods on the RAM Legacy Stock Assessment Database
--- a compilation of stock-assessment output from hundreds of exploited marine
populations around the world. Our analysis of the stock-assessment database was
based on version 2.5. After removing stocks for which at least one of the
individual models did not converge (121), this database
included `r ram_stocks_n` stocks. We removed these stocks for all methods ---
both for the individual and superensemble models. An alternative would be to
fit separate superensemble models to subsets of the individual models that did converge,
but for simplicity we only used superensemble models fitted to all four
individual models.\R{A6}

@@

<!-- It is often important to provide measures of uncertainty with quantitative -->
<!-- estimates. --> 
\R{B}
We illustrated that superensembles can improve point
estimates of status and trends in status; however, there is no reason why
superensembles cannot also be used to
provide measures of uncertainty around those point estimates. 
First, the same approaches to deriving measures of uncertainty from any regression model are available to a superensemble. 
For example, likelihood profile confidence intervals or Bayesian credible intervals 
are available for superensembles fit via maximum likelihood or Bayesian procedures.
Measures of predictive uncertainty can be generated for machine learning
methods such as random forests or GBMs using 
bootstrap procedures [e.g. @hastie2009; @finnegan2015].
Furthermore, uncertainty from the component models could 
be included in superensembles.
These superensembles could be fit using any errors-in-variables or
measurement-error modelling approach [e.g. @carroll2006]

@@

A strength of superensembles is that they can be tailored to predict specific
response variables. For example, we built separate superensemble models of mean
$B/B_\mathrm{MSY}$ and the slope of $B/B_\mathrm{MSY}$. The same set of model
weights or non-linear relationships need not hold across different response
variables. For instance, SSCOM contributed little to the GBM superensemble
estimate of status at higher levels of predicted $B/B_\mathrm{MSY}$ (Fig.
\ref{partial-sim}), but contributed strongly to estimates of trend (Fig.
\ref{partial-sim-slope}). Formally, fitting superensemble models to specific
quantities of interest (such as the slope of $B/B_\mathrm{MSY}$) provides an additional
calibration step to a quantity of interest [@rykiel1996].\R{A10}
This ensemble calibration could include a loss function
tailored to the goals of the model, say placing greater weight on accuracy at
lower rather than higher status levels. Conversely, because superensembles are
tailored to a specific response and loss function, superensembles force a
modeller to choose an operational purpose for their model upfront [*sensu*
@dickey-collas2014]. For instance, one could have an ensemble 
estimate of $B$ and an ensemble estimate of $B_0$, but their
ratio may not be the same as an ensemble estimate of $B/B_0$.
A modeller might therefore choose to focus on $B/B_0$, 
which provides a unitless ratio, is easier to compare across stocks, 
and the ratio is often a more stable estimate across models [@deroba2015].

As @box1987 noted, all models are wrong, but some may still be useful. The
ensemble methods we investigated attempt to piece together the useful parts of
candidate models to build a model with improved performance. Instead of viewing
the superensemble as a black box, we think considerable mechanistic
understanding can be gained by studying its structure. For example, when SSCOM
estimates low status this is likely the case, conversely when COMSIR
estimates low status, the true status is more likely to be high (Fig.
\ref{partial-sim}). These models have two main differences: (1) the form of
effort dynamics and (2) the allowance for both measurement and process error in
SSCOM, whereas the implemented COMSIR admits measurement error only. Were the
methods to differ only in effort dynamics, the results point towards a more
suitable representation of effort dynamics at low biomasses in SSCOM. We think
that such investigation of the structure of a superensemble may lead to
improvement in the mechanisms assumed in individual models.

@@

\R{A}Superensembles can help address some longstanding
issues in fisheries science.
For example, superensembles assist by not needing to decide on one model ---
instead of deciding on dome versus asymptotic fisheries 
selectivity [e.g., @sampson2012], 
or on whether to fix or estimate natural mortality [e.g., @johnson2014],
superensembles can use multiple models to draw inference.
Furthermore, the relative contributions of individual models can help tease apart 
the conditions under which various model assumptions 
result in the most accurate predictions.
Finally, superensembles can be used to directly 
estimate other quantities of interest in fisheries science. 
For instance, superensembles could be used to estimate 
fishing mortality compared to fishing mortality at MSY ($F/F_\mathrm{MSY}$)
or a fisheries selectivity curve parameter.
However, superensembles are not a panacea 
and are ultimately limited by the quality, breadth, and representativeness
of simulated or trusted data to which superensembles are calibrated.

@@

We thank members of Phase I of the working group "Developing new approaches to
global stock status assessment and fishery production potential of the seas"
who contributed to developing the data-limited methods and simulations used in
our analysis. We thank E. Jardim, F. Scott, and J.A. Hutchings for helpful
comments during the development of this project, and R.D. Methot for comments
on an earlier version of the manuscript. We thank
the Gordon and Betty Moore Foundation for funding the working group "Applying
data-limited stock status models and developing management guidance for
unassessed fish stocks".
